From Reversible Programs to \\ Univalent Universes and Back

### 2021-07-01 Pi+/paper/reversible1.tex
clean up a bit early parts

%%%%%%%%%
\subsection{Denotational Semantics (Outline)}

@@

%%%%%%%%%
\subsection{Examples}
\label{sec:langRev-examples}
\label{examples}

\noindent The input value of type $\mathbb{2} \times A$ is processed by the distribute operator \ensuremath{\dist},
which converts it into a value of type $(\onet \times A) + (\onet \times A)$. In the \ensuremath{\mathit{left}} branch,
which corresponds to the case when the boolean is \ensuremath{\mathit{false}}, the combinator~\ensuremath{c_1} is
applied to the value of type~\ensuremath{A}. The right branch which corresponds to the boolean being
\ensuremath{\mathit{true}} passes the value of type $A$ through the combinator \ensuremath{c_2}.  The inverse of
\ensuremath{\dist}, namely \ensuremath{\factor} is applied to get the final result. The full expressiveness of $\Pi$ is
demonstrated by the following implementation of $\Afun{cnot}$ and $\Afun{toffoli}$ which are universal for reversible
computation~\cite{Toffoli:1980}. The $\Afun{cnot}$ gates takes two input bits: a control bit and a target bit, and
negates the target bit if the control bit is set. It is essentially a one-branch version of $\Afun{cif}$ above. The
Toffoli gate generalizes the idea to a gate that takes 3 input bits: 2 control bits and one target bit: boolean inputs:
it negates the target bit if both control bits are set.

>>>>

%%%%%%%%%
\subsection{Informal Semantics and Examples}
\label{sec:langRev-examples}
\label{examples}

\noindent The input value of type $\mathbb{2} \times A$ is processed by the distribute operator \ensuremath{\dist},
which converts it into a value of type $(\onet \times A) + (\onet \times A)$. In the \ensuremath{\mathit{left}} branch,
which corresponds to the case when the boolean is \ensuremath{\mathit{false}}, the combinator~\ensuremath{c_1} is
applied to the value of type~\ensuremath{A}. The right branch which corresponds to the boolean being
\ensuremath{\mathit{true}} passes the value of type $A$ through the combinator \ensuremath{c_2}.  The inverse of
\ensuremath{\dist}, namely \ensuremath{\factor} is applied to get the final result. The full expressiveness of $\Pi$ is
demonstrated by an implementation of $\Afun{cnot}$ and $\Afun{toffoli}$ which are universal for reversible
computation~\cite{Toffoli:1980}. The $\Afun{cnot}$ gates takes two input bits: a control bit and a target bit, and
negates the target bit if the control bit is set. It is essentially a one-branch version of $\Afun{cif}$ above. The
Toffoli gate generalizes the idea to a gate that takes 3 input bits: 2 control bits and one target bit: boolean inputs:
it negates the target bit if both control bits are set.

%%%%%%%%%
\subsection{Denotational Semantics}

@@
